\documentclass[10pt]{article}

\RequirePackage{fontspec}
\setmainfont[
BoldFont={Baskerville SemiBold},
ItalicFont={Baskerville Italic},
BoldItalicFont={Baskerville SemiBold Italic}
]{Baskerville}

\usepackage[
  margin=1in,
  paperwidth=8.5in,
  paperheight=11in
]{geometry}

\pagenumbering{gobble}
\usepackage[hidelinks]{hyperref}
\urlstyle{same}

\usepackage{etoolbox}
\newtoggle{MODEPLT}
\newtoggle{MODELONG}

\togglefalse{MODEPLT}
\togglefalse{MODELONG}

\newcommand{\SectionTitle}[2][.2in] {
  \vspace{#1}
  \textbf{\large #2}
  \vspace{.1in}
}

\newcommand{\Entry}[3] {
  \noindent \textit{\strong{#1}, #2} \hfill \textit{#3}
}

\newcommand{\DescribedEntry}[5][.035in] {
  \noindent \textit{\strong{#2}, #3} \hfill \textit{#4}
  \vspace{#1}
  % \vspace{.035in}

  #5\leavevmode\\
}

\newcommand{\DescribedEntryLine}[4] {
  \noindent \textit{\strong{#1}, #2} \hfill \textit{#3}
  \vspace{.035in}

  #4 \\
}

\newcommand{\DescribedEntryTitle}[3] {
  \noindent \textit{\strong{#1}, #2} \hfill \textit{#3}
  \\
}

\begin{document}
\begin{flushleft}

\huge{Marcos Minond} \normalsize
\hfill \href{https://minond.xyz}{https://minond.xyz} \\
\hfill \href{https://github.com/minond}{https://github.com/minond}

\normalsize


\SectionTitle[.025in]{Summary}

I'm a software engineer with over a decade of experience. I specialize in creating performant, scalable solutions that exceed user expectations. My technical expertise is complemented by a strong commitment to community service, exemplified by my ongoing role as an organizer and instructor at the Utah Refugee Center, where I mentor aspiring developers.

\vspace{.1in}

I'm deeply passionate about software design and architecture, distributed systems, and PLT. What I value most from my place of work is: the people that I work with, the products or services we're providing, and the technical challenges we're solving. I'm eager to find a place where these elements converge.

% My career highlights include leading the development of a financial feed product that secured a \$3 million contract and optimizing critical endpoints to reduce response times significantly.

% \vspace{.08in}
%
% My technical expertise is complemented by a strong commitment to community service, exemplified by my ongoing role as an organizer and instructor at the Utah Refugee Center, where I mentor aspiring developers. I'm passionate about software design and system architecture, I seek opportunities to drive innovation and efficiency in challenging environments.

\SectionTitle{Skills}

% \begin{itemize}
%   \setlength\itemsep{.0in}
%   \item \textbf{Programming Languages:} Scala, Racket, Ruby, Python, Go, TypeScript/JavaScript, Elm.
%   \item \textbf{Frameworks \& Libraries:} FastAPI, Rails, Node.js, React.
%   \item \textbf{Databases:} Proficient in database and query optimization techniques.
%   \item \textbf{Development Tools:} Bash, Linux, Git, Continuous Integration tools.
%   \item \textbf{Software Engineering:} Experienced in software design, system architecture, compilers, parsing, and code generation.
%   \item \textbf{DevOps:} Knowledgeable in process automation, continuous integration, and distributed systems.
%   \item \textbf{Soft Skills:} Strong project management capabilities, effective in observability and monitoring, excellent mentorship and team leadership skills.
% \end{itemize}

% Python, Scala, Racket, Ruby, Go, TypeScript/JavaScript, Node, Elm, database and query optimization, bash, Linux, software design, system architecture, compilers, parsing, codegen, process automation, continuous integration, distributed systems, observability, project management.

Python, Scala, Racket, Ruby, Go, TypeScript/JavaScript, Elm. Bash, Linux, git, CI/CD. Experienced in web application development, software design, system architecture, compilers, parsing, code generation, distributed systems, observability and monitoring. Proficient in database and query optimization techniques. Strong project management capabilities, excellent mentorship and team leadership skills.

\iftoggle{MODEPLT}{
  \SectionTitle{Independent Work}

  I've independently developed compilers and programming languages featuring Hindley–Milner type inference, custom opcode instruction sets, multi-pass compilation, and integration with LLVM. My projects demonstrate experience and knowledge in formal language specifications, parsing, syntax and semantic analysis, and code generation.
  \\
}

\SectionTitle{Experience}

\DescribedEntryTitle{Director of Engineering}{Voze}{October 2023 - Present}
\vspace{.1in}
\DescribedEntryTitle{Software Engineer, Freelance}{Minond, LLC}{January 2023 - October 2023}
% \DescribedEntry{Software Engineer, Freelance}{Minond, LLC}{January 2023 - Present}{
%   I've engaged in diverse projects encompassing personal initiatives and contract work. My primary focus has been on building a carbon footprint application for a client, where I have played a pivotal role in the design, development, and deployment of the application.
% }
\vspace{.1in}
\DescribedEntry[-0.05in]{Staff Software Engineer}{MX}{April 2018 - December 2022}{
  \begin{itemize}
    \setlength\itemsep{.0in}
    \item Technical lead to over a dozen backend and frontend engineers in the design and development of MXinsights, a financial feed product serving over 7 million users at the time of my departure. This product helped us to break into a new market by securing a contract exceeding \$3 million with one of Canada's largest banks.
    \item Member of the Enterprise Technical Office group where I dealt with high urgency client requirements and advised in project architecture and problem solving platform-wide.
    \item Conceived and led initiative to improve our client's developer experience, shortening part of the implementation process from an average of two weeks down to 6 hours. This included building SDKs for major mobile platforms. Evangelized this team's solutions and enhancements to internal and external parties.
    \item Optimized critical endpoints, reducing average response times from 100ms to under 10ms. These endpoints served as the backbone for the entire platform and are used by all of our products.
    \item Played an active part in shaping our platform as both an individual contributor and a mentor to individuals and teams designing and developing solutions for a rapidly evolving industry and ecosystem.
  \end{itemize}
}
\vspace{.02in}
\iftoggle{MODELONG}{
  \DescribedEntry{Software Engineer, Freelance}{Minond, LLC}{May 2017 - April 2018}{
    Helped companies dismantle and analyze problems, develop and vet new ideas and solutions, and build mission-critical products.
  }
}{
  \DescribedEntryTitle{Software Engineer, Freelance}{Minond, LLC}{May 2017 - April 2018}
}
\vspace{.1in}
\iftoggle{MODELONG}{
  \DescribedEntry{Software Engineer, Tech Lead}{Domo, Inc.}{December 2014 - May 2017}{
    I started at Domo working on new features as a front-end engineer. I worked on a new zero state experience for the product, a report builder and scheduler, and more. I then joined another team as a backend Scala engineer and later became that team's lead. Got to learn a lot in this position, such as why good logging is a wonderful thing.
  }
}{
  \DescribedEntryTitle{Software Engineer, Tech Lead}{Domo, Inc.}{December 2014 - May 2017}
}
\vspace{.1in}
\iftoggle{MODELONG}{
  \DescribedEntry{Software Engineer, Team Lead}{InsideSales.com}{January 2014 - November 2014}{
    Lead of the PowerStandings team. Worked with my team to making the MVP production ready, improving the interface and user experience, and making the application standalone.
  }
  \vspace{.1in}
  \DescribedEntry{Software Engineer, DevOps}{InsideSales.com}{June 2013 - January 2014}{
    Worked on bring in a more "DevOps-y" mindset into the department. Helped improve the development and deployment process for lots of services. Learned a lot about ops, systems, Linux.
  }
  \vspace{.1in}
  \DescribedEntry{Software Engineer}{InsideSales.com}{January 2012 - June 2013}{
    I worked on new features for our LMP product. Some of these were a custom report engine and an intelligent data deduplication tool. The Intelligent Deduplication project was one of my favorites. It was able to take a client's database, search for duplicate records by comparing multiple data points, then merge all the data, which spanned across multiple tables, into a new record.
  }
  \vspace{.1in}
  \DescribedEntry{Implementation Team Manager}{InsideSales.com}{January 2011 - December 2011}{
    I managed a team of Implementation Technicians. As a team we made further improvements to my previous work. One of the biggest takeaways from this position was that I learned how to breakdown big jobs into smaller tasks so that they could be worked on by a team.
  }
  \vspace{.1in}
  \DescribedEntry{Implementation Team Member}{InsideSales.com}{January 2009 - December 2010}{
    I joined the department when it was first being created, so I was a big part in helping the department grow. I helped by creating the processes and standards that would later be followed by the team I managed. This was my first exposure to a professional environment, and it was a great learning experience. This is also the job that got me interested in programming.
  }
}{
  \DescribedEntryTitle{Software Engineer}{InsideSales.com}{January 2012 - November 2014}
  \vspace{.1in}
  \DescribedEntryTitle{Implementation Team Member \& Manager}{InsideSales.com}{January 2009 - December 2011}
}

\SectionTitle{Education}

\Entry{Utah Valley University}{BS, Computer Science (Incomplete)}{2009 - 2013}


\SectionTitle{Volunteering}

\DescribedEntryLine{Programming Class Organizer \& Instructor}{Utah Department of Workforce Services}{2016 - Present}{
  I organize and teach programming classes for refugees and my local refugee center.
}

\end{flushleft}
\end{document}
